
\begin{longtabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\hline
Indicator code & Name & Description & Source & Source organisation\\
\hline
AG.LND.TOTL.K2 & Land area (sq. km) & Land area is a country's total area, excluding area under inland water bodies, national claims to continental shelf, and exclusive economic zones. In most cases the definition of inland water bodies includes major rivers and lakes. & World Development Indicators & Food and Agriculture Organization, electronic files and web site.\\
\hline
BG.GSR.NFSV.GD.ZS & Trade in services (\% of GDP) & Trade in services is the sum of service exports and imports divided by the value of GDP, all in current U.S. dollars. & World Development Indicators & International Monetary Fund, Balance of Payments Statistics Yearbook and data files, and World Bank and OECD GDP estimates.\\
\hline
EN.ATM.CO2E.PC & CO2 emissions (metric tons per capita) & Carbon dioxide emissions are those stemming from the burning of fossil fuels and the manufacture of cement. They include carbon dioxide produced during consumption of solid, liquid, and gas fuels and gas flaring. & World Development Indicators & Emissions data are sourced from Climate Watch Historical GHG Emissions (1990-2020). 2023. Washington, DC: World Resources Institute. Available online at: https://www.climatewatchdata.org/ghg-emissions\\
\hline
GC.TAX.INTT.RV.ZS & Taxes on international trade (\% of revenue) & Taxes on international trade include import duties, export duties, profits of export or import monopolies, exchange profits, and exchange taxes. & World Development Indicators & International Monetary Fund, Government Finance Statistics Yearbook and data files.\\
\hline
GC.TAX.TOTL.GD.ZS & Tax revenue (\% of GDP) & Tax revenue refers to compulsory transfers to the central government for public purposes. Certain compulsory transfers such as fines, penalties, and most social security contributions are excluded. Refunds and corrections of erroneously collected tax revenue are treated as negative revenue. & World Development Indicators & International Monetary Fund, Government Finance Statistics Yearbook and data files, and World Bank and OECD GDP estimates.\\
\hline
NE.TRD.GNFS.ZS & Trade (\% of GDP) & Trade is the sum of exports and imports of goods and services measured as a share of gross domestic product. & World Development Indicators & World Bank national accounts data, and OECD National Accounts data files.\\
\hline
NV.IND.MANF.ZS & Manufacturing, value added (\% of GDP) & Manufacturing refers to industries belonging to ISIC divisions 15-37. Value added is the net output of a sector after adding up all outputs and subtracting intermediate inputs. It is calculated without making deductions for depreciation of fabricated assets or depletion and degradation of natural resources. The origin of value added is determined by the International Standard Industrial Classification (ISIC), revision 3. Note: For VAB countries, gross value added at factor cost is used as the denominator. & World Development Indicators & World Bank national accounts data, and OECD National Accounts data files.\\
\hline
NV.IND.TOTL.KD & Industry (including construction), value added (constant 2015 US\$) & Industry (including construction) corresponds to ISIC divisions 05-43 and includes manufacturing (ISIC divisions 10-33). It comprises value added in mining, manufacturing (also reported as a separate subgroup), construction, electricity, water, and gas. Value added is the net output of a sector after adding up all outputs and subtracting intermediate inputs. It is calculated without making deductions for depreciation of fabricated assets or depletion and degradation of natural resources. The origin of value added is determined by the International Standard Industrial Classification (ISIC), revision 4. Data are in constant 2015 prices, expressed in U.S. dollars. & World Development Indicators & World Bank national accounts data, and OECD National Accounts data files.\\
\hline
NV.IND.TOTL.ZS & Industry (including construction), value added (\% of GDP) & Industry (including construction) corresponds to ISIC divisions 05-43 and includes manufacturing (ISIC divisions 10-33). It comprises value added in mining, manufacturing (also reported as a separate subgroup), construction, electricity, water, and gas. Value added is the net output of a sector after adding up all outputs and subtracting intermediate inputs. It is calculated without making deductions for depreciation of fabricated assets or depletion and degradation of natural resources. The origin of value added is determined by the International Standard Industrial Classification (ISIC), revision 4. Note: For VAB countries, gross value added at factor cost is used as the denominator. & World Development Indicators & World Bank national accounts data, and OECD National Accounts data files.\\
\hline
NY.GDP.COAL.RT.ZS & Coal rents (\% of GDP) & Coal rents are the difference between the value of both hard and soft coal production at world prices and their total costs of production. & World Development Indicators & World Bank staff estimates based on sources and methods described in the World Bank's The Changing Wealth of Nations.\\
\hline
NY.GDP.FRST.RT.ZS & Forest rents (\% of GDP) & Forest rents are roundwood harvest times the product of regional prices and a regional rental rate. & World Development Indicators & World Bank staff estimates based on sources and methods described in the World Bank's The Changing Wealth of Nations.\\
\hline
NY.GDP.MINR.RT.ZS & Mineral rents (\% of GDP) & Mineral rents are the difference between the value of production for a stock of minerals at world prices and their total costs of production. Minerals included in the calculation are tin, gold, lead, zinc, iron, copper, nickel, silver, bauxite, and phosphate. & World Development Indicators & World Bank staff estimates based on sources and methods described in the World Bank's The Changing Wealth of Nations.\\
\hline
NY.GDP.NGAS.RT.ZS & Natural gas rents (\% of GDP) & Natural gas rents are the difference between the value of natural gas production at regional prices and total costs of production. & World Development Indicators & World Bank staff estimates based on sources and methods described in the World Bank's The Changing Wealth of Nations.\\
\hline
NY.GDP.PCAP.CD & GDP per capita (current US\$) & GDP per capita is gross domestic product divided by midyear population. GDP is the sum of gross value added by all resident producers in the economy plus any product taxes and minus any subsidies not included in the value of the products. It is calculated without making deductions for depreciation of fabricated assets or for depletion and degradation of natural resources. Data are in current U.S. dollars. & World Development Indicators & World Bank national accounts data, and OECD National Accounts data files.\\
\hline
NY.GDP.PCAP.KD & GDP per capita (constant 2015 US\$) & GDP per capita is gross domestic product divided by midyear population. GDP is the sum of gross value added by all resident producers in the economy plus any product taxes and minus any subsidies not included in the value of the products. It is calculated without making deductions for depreciation of fabricated assets or for depletion and degradation of natural resources. Data are in constant 2015 U.S. dollars. & World Development Indicators & World Bank national accounts data, and OECD National Accounts data files.\\
\hline
NY.GDP.PCAP.KD.ZG & GDP per capita growth (annual \%) & Annual percentage growth rate of GDP per capita based on constant local currency. GDP per capita is gross domestic product divided by midyear population. GDP at purchaser's prices is the sum of gross value added by all resident producers in the economy plus any product taxes and minus any subsidies not included in the value of the products. It is calculated without making deductions for depreciation of fabricated assets or for depletion and degradation of natural resources. & World Development Indicators & World Bank national accounts data, and OECD National Accounts data files.\\
\hline
NY.GDP.PETR.RT.ZS & Oil rents (\% of GDP) & Oil rents are the difference between the value of crude oil production at regional prices and total costs of production. & World Development Indicators & World Bank staff estimates based on sources and methods described in the World Bank's The Changing Wealth of Nations.\\
\hline
NY.TTF.GNFS.KN & Terms of trade adjustment (constant LCU) & The terms of trade effect equals capacity to import less exports of goods and services in constant prices. Data are in constant local currency. & World Development Indicators & World Bank national accounts data, and OECD National Accounts data files.\\
\hline
SP.POP.TOTL & Population, total & Total population is based on the de facto definition of population, which counts all residents regardless of legal status or citizenship. The values shown are midyear estimates. & World Development Indicators & (1) United Nations Population Division. World Population Prospects: 2022 Revision. (2) Census reports and other statistical publications from national statistical offices, (3) Eurostat: Demographic Statistics, (4) United Nations Statistical Division. Population and Vital Statistics Reprot (various years), (5) U.S. Census Bureau: International Database, and (6) Secretariat of the Pacific Community: Statistics and Demography Programme.\\
\hline
\end{longtabu}
